|

### 2022-01-04 text/ManuscriptDraft.Rmd
Manuscript update. DBSCAN.

\newpage

@@

Here, we show that information on phenology at the level of individuals can be derived from image-based monitoring of flower phenology. Further, we present and evaluate an automatic flower tracking algorithm.

@@

@@

Manually annotating a subset of the objects in the image series could help derive a good set of parameters.

When deploying the tracking algorithm on naive data that has not been manually tracked, it is not possible to

@@

Online tracking:
SORT
DeepSORT

>>>>

@@

Here, we show that information on phenology at the level of individuals can be derived from image-based monitoring of flower phenology. Further, we present and evaluate an automatic flower tracking and filtering algorithm.

Tracking individual flowers enables the possibility of assigning reproductive success to the individual, for example by observation of seed set. Thereby, it can be explored whether reproductive success is affected by timing and length of flowering. By simultaneously tracking flower visits, these could be assigned to the individual flower and visitation rates per flower could be calculated per flower and related to reproductive success. Further, any information of taxonomic grouping could refine this analyses.

For complex scenes with many flowers in close vicinity to each other, we suggest a conservative filtering approach. The approach may remove correct tracks, but the tracks that remain will have a lower risk of tracking errors. The approach allows for more confidence in upscaling the method. E.g., when running the method on a large number of image series, it is preferable to extract individual high-confidence tracks from each series and ignore the remaining tracks.

@@

Depending on the nature of the objects being tracked and the complexity of the scene, the user parameters can be estimated from visual examination of the tracking results. Often it may be preferable to manually annotate a subset of the objects in the image series and derive a set of user parameters from these results.

@@

When deploying the automatic tracking algorithm on naive data without ground truth tracks, it is not possible to manually filter for correct tracks. Therefore, we present a conservative filtering method that extracts the most trustworthy tracks from a scene.

We then apply the DBSCAN clustering algorithm on these track geometrics to remove tracks in areas with a high density of tracks as these have a high risk of tracking mismatches. Second, we filter overlapping tracks using the following approach.

@@

Tracking Multiple Moving Objects Using Unscented Kalman
Filtering Techniques:
"Kalman filtering (KF) [5] is widely used to track moving objects, with which we
can estimate the velocity and even acceleration of an object with the measurement of its locations.
However, the accuracy of KF is dependent on the assumption of linear motion for any object to be
tracked. If an object takes some abrupt turns, the nonlinear movement cannot be well handled by the
KF framework (due to the linear movement assumption of the design of KF)."
Kalman, R. E. A New Approach to Linear Filtering and Prediction Problems. Journal of Basic
Engineering, 1960(82), pp. 35-45.
